---
title: "Exercise 10 - EPI536-Assignments"
author: "Matthew Hoctor"
date: "7/117/2021"
output:
  html_document:
    number_sections: no
    theme: lumen
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(engine.path = list(
  stata = "C:/Program Files/Stata17/StataBE-64"
))
```

```{r libraries, include=FALSE}
library(Statamarkdown)
```

# A: Selection

Use the selection approach to identify confounders of the association between food assistance and high waist circumference among food secure boys.

## 1

Fit the crude model, modeling high waist circumference as a function of food assistance only.  You have used the code needed Exercise 8.  In the table below A.3, record the odds ratios (OR) for food assistance and its 95% confidence interval. Separate the confidence interval bounds with a comma. Report these measures to 2 decimal places. 

```{stata}
use "NHANES0708_all.dta"
svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any
xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any,or
```

## 2

Fit the remaining models, modeling high waist circumference as a function of food assistance plus one potential confounder at a time as shown in the table below A.3.  Record OR for food assistance and its 95% CI from each model in rows b, c, and d. 

### b: age (ridageyr)

```{stata}
use "NHANES0708_all.dta"
svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any ridageyr
xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any ridageyr,or
```

### c: race/ethnicity (race_eth)

```{stata}
use "NHANES0708_all.dta"
svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any i.race_eth
xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any i.race_eth,or
```

### d: health insurance (hinsur)

```{stata}
use "NHANES0708_all.dta"
svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any i.hinsur
xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any i.hinsur,or
```

## 3

Calculate the percent change in each OR from b, c, and d, compared to the OR in a.  Enter these into the last column. Report the % change in OR to 1 decimal, retaining the sign.

## 4

### hinsur 

```{stata}
use "NHANES0708_all.dta"
svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any i.race_eth i.hinsur
xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any i.race_eth i.hinsur,or
```

### ridageyr

```{stata}
use "NHANES0708_all.dta"
svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any i.race_eth ridageyr
xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any i.race_eth ridageyr,or
```

### hinsur + ridageyr

```{stata}
use "NHANES0708_all.dta"
svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any i.race_eth i.hinsur ridageyr
xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any i.race_eth i.hinsur ridageyr,or
```

# B Deletion

## 1 Cycle 1

### Full model

```{stata}
use "NHANES0708_all.dta"
svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata food_any ridageyr i.race_eth fpl_2cat i.hinsur pr_male i.pr_ed3 i.pr_age
xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata food_any ridageyr i.race_eth fpl_2cat i.hinsur pr_male i.pr_ed3 i.pr_age,or
```

### Delete ridageyr

```{stata}
use "NHANES0708_all.dta"
svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata food_any i.race_eth fpl_2cat i.hinsur pr_male i.pr_ed3 i.pr_age
xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata food_any i.race_eth fpl_2cat i.hinsur pr_male i.pr_ed3 i.pr_age,or
```


### Delete race_eth

```{stata}
use "NHANES0708_all.dta"
svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata food_any ridageyr fpl_2cat i.hinsur pr_male i.pr_ed3 i.pr_age
xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata food_any ridageyr fpl_2cat i.hinsur pr_male i.pr_ed3 i.pr_age,or
```


### delete hinsur

```{stata}
use "NHANES0708_all.dta"
svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata food_any ridageyr i.race_eth fpl_2cat pr_male i.pr_ed3 i.pr_age
xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata food_any ridageyr i.race_eth fpl_2cat pr_male i.pr_ed3 i.pr_age,or
```

## 2 Deletion cycle 2&3

### Base Model: Delete ridageyr

```{stata}
use "NHANES0708_all.dta"
svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata food_any i.race_eth fpl_2cat i.hinsur pr_male i.pr_ed3 i.pr_age
xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata food_any i.race_eth fpl_2cat i.hinsur pr_male i.pr_ed3 i.pr_age,or
```

### Delete hinsur (full -A1 -A2)

```{stata}
use "NHANES0708_all.dta"
svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata food_any i.race_eth fpl_2cat pr_male i.pr_ed3 i.pr_age
xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata food_any i.race_eth fpl_2cat pr_male i.pr_ed3 i.pr_age,or
```

### Delete race_eth

```{stata}
use "NHANES0708_all.dta"
svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata food_any fpl_2cat i.hinsur pr_male i.pr_ed3 i.pr_age
xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata food_any fpl_2cat i.hinsur pr_male i.pr_ed3 i.pr_age,or
```

### Delete ridageyr & hinsur & race_eth (full -A1 -A2 -A3)

```{stata}
use "NHANES0708_all.dta"
svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata food_any fpl_2cat pr_male i.pr_ed3 i.pr_age
xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata food_any fpl_2cat pr_male i.pr_ed3 i.pr_age,or
```

# C Comparison of Selection & Deletion

# D Review

# Bonus

## Unadjusted

```{stata}
use "NHANES0708_all.dta"
svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any
xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any,or
```

## age (ridageyr)

```{stata}
use "NHANES0708_all.dta"
svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any ridageyr
xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any ridageyr,or
```

## quadratic age


```{stata}
use "NHANES0708_all.dta"
svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

gen agec=ridageyr-10.2
gen agec_sq=agec^2
gen agec_cb=agec^3

xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any agec agec_sq
xi: svy,subpop(if subpop2==1 & male==1 & foodinsec==0): logit wccata i.food_any agec agec_sq,or
```


