---
title: "Exercise 5 - EPI536-Assignments"
author: "Matthew Hoctor"
date: "7/4/2021"
output:
  html_document:
    number_sections: no
    theme: lumen
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(engine.path = list(
  stata = "C:/Program Files/Stata17/StataBE-64"
))
```

```{r libraries, include=FALSE}
library(Statamarkdown)
```

# 2: Age & FPL criteria

## a: age criteria

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_merged.dta"

bysort age_instudy: su ridageyr
ta age_instudy
```

Repeating the above analysis with the dataset provided in class:

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_newvars.dta"

bysort age_instudy: su ridageyr
ta age_instudy
```

## b: FPL criteria

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_merged.dta"

bysort fpl_instudy: su indfmpir
ta fpl_instudy
```

Repeating the above analysis with the dataset provided in class:

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_newvars.dta"

bysort fpl_instudy: su indfmpir
ta fpl_instudy
```

# 3: tabulation of both study inclusion criteria

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_merged.dta"

gen subpop1=0
	replace subpop1=1 if age_instudy==1 & fpl_instudy==1
ta subpop1

label define subpop1 0 "No" 1 "Yes"
label values subpop1 subpop1
label variable subpop1 "Meets Inclusion Criteria"
ta subpop1

save,replace
```

Repeating the above analysis with the dataset provided in class:

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_newvars.dta"

gen subpop1=0
	replace subpop1=1 if age_instudy==1 & fpl_instudy==1
ta subpop1

label define subpop1 0 "No" 1 "Yes"
label values subpop1 subpop1
label variable subpop1 "Meets Inclusion Criteria"
ta subpop1

save,replace
```

# 4: complete data on exposure variables and outcome variables

## for missing outcome (dependant) variables

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_merged.dta"

gen miss_dv=missing(bmxbmi, bmxwaist)
ta subpop1 miss_dv

label define miss_dv 0 "No" 1 "Yes"
label values miss_dv miss_dv
label variable miss_dv "Missing Dependent Variables"
ta subpop1 miss_dv
ta miss_dv

save,replace
```

Repeating the above analysis with the dataset provided in class:

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_newvars.dta"

gen miss_dv=missing(bmxbmi, bmxwaist)
ta subpop1 miss_dv

label define miss_dv 0 "No" 1 "Yes"
label values miss_dv miss_dv
label variable miss_dv "Missing Dependent Variables"
ta subpop1 miss_dv

save,replace
```

## For missing exposure (independant) variables

The data file from E4 does not have the variables necessary (food_stamp, WIC, school_meal, foodinsec).

Repeating the above analysis with the dataset provided in class:

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_newvars.dta"

gen miss_iv=missing(food_stamp, WIC, school_meal, foodinsec)
ta food_stamp miss_iv,m
ta WIC miss_iv,m
ta school_meal miss_iv,m
ta foodinsec miss_iv,m

label define miss_iv 0 "No" 1 "Yes"
label values miss_iv miss_iv
label variable miss_iv "Missing Independent Variables"
ta subpop1 miss_iv

save,replace
```

# 5: creating a variable to indicate complete data and meets inclusion criteria

Continuing on using only the dataset provided in class:

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_newvars.dta"

gen subpop2=0
	replace subpop2=1 if subpop1==1 & miss_iv==0 & miss_dv==0
ta subpop2

label define subpop2 0 "No" 1 "Yes"
label values subpop2 subpop2
label variable subpop2 "Meets Inclusion Criteria & No Missing values"
ta subpop2

save,replace
```

# 6 Calculating number remaining at each step

## <= 200% FPL

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_newvars.dta"
ta fpl_instudy age_instudy
```

## missing primary outcome (BMI)

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_newvars.dta"

gen miss_bmi=missing(bmxbmi)
ta subpop1 miss_bmi
```

## missing secondary outcome (waist circumfrence, WC)

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_newvars.dta"

gen miss_bmi=missing(bmxbmi)
gen miss_waist=missing(bmxwaist)
ta subpop1 miss_waist if miss_bmi==0
```

## missing primary exposure (Food stamps; WIC; free/reduced school meals)

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_newvars.dta"

ta miss_iv miss_dv if subpop1==1
```

## Missing Effect Modifier (food security)

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_newvars.dta"

ta fsdch if subpop2==1
```

## missing Gender or Age

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_newvars.dta"

ta ridageyr if subpop2==1
ta riagendr if subpop2==1
```

## missing health insurance

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_newvars.dta"

ta hinsur if subpop2==1
```

## Missing primary respondent gender, age, or education

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_newvars.dta"

ta pr_ed3 if subpop2==1
```


