---
title: "Exercise 6 - EPI536-Assignments"
author: "Matthew Hoctor"
date: "7/6/2021"
output:
  html_document:
    number_sections: no
    theme: lumen
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(engine.path = list(
  stata = "C:/Program Files/Stata17/StataBE-64"
))
```

```{r libraries, include=FALSE}
library(Statamarkdown)
library(haven)
```

# 1: Comparing age among boys with and without food assistance

## a: Correcting for clustered/stratified sampling and survey weights

```{stata}
use "NHANES0708_all.dta"

svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)
svy, subpop(if subpop2==1 & male==1): mean ridageyr,over(food_any)coeflegend
svy, subpop(if subpop2==1 & male==1): mean ridageyr,over(food_any)

test _b[c.ridageyr@0bn.food_any] =_b[c.ridageyr@1.food_any]
```

## b: Correcting for clustered/stratified sampling, but not survey weights

```{stata}
use "NHANES0708_all.dta"

svyset sdmvpsu, strata(sdmvstra)
svy,subpop(if subpop2==1 & male==1): mean ridageyr,over(food_any)

test _b[c.ridageyr@0bn.food_any] =_b[c.ridageyr@1.food_any]
```

## c: Ignoring survey sampling

```{stata}
use "NHANES0708_all.dta"

svyset

ttest ridageyr if subpop2==1 & male==1,by(food_any)
```

# 2: Comparing race/ethnicity among boys with and without food assistance

## a: Correcting for clustered/stratified sampling and survey weights

```{stata}
use "NHANES0708_all.dta"

svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)
svy, subpop(if subpop2==1 & male==1): ta race_eth food_any,col percent
```

## b: Correcting for clustered/stratified sampling, but not survey weights

```{stata}
use "NHANES0708_all.dta"

svyset sdmvpsu, strata(sdmvstra)
svy, subpop(if subpop2==1 & male==1): ta race_eth food_any,col percent
```

## c: Ignoring survey sampling

```{stata}
use "NHANES0708_all.dta"

svyset

ta race_eth food_any if subpop2==1 & male==0,col chi2
```

# 3: Exporting data

```{stata}
use "NHANES0708_all.dta"

svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)
tabout race_eth food_any if subpop2==1 & male==1 using "Tabout.csv", c(col) f(2) svy replace
tabout food_any if subpop2==1 & male==1 using "Tabout.csv", c(mean ridageyr se) f(2) sort sum svy append
```

# 4: Replicate Table 1, Boys

 a: Counts are unweighted (practice using the tabout command to generate weighted column percentages with one line of code)
 b: Report mean ± SE (the “mean ± SD” label is incorrect in the paper) (practice using the tabout command to generate weighted means ± se for continuous variables)
c: Discrepancies of counts of overweight & Obese There are minor discrepancies of the counts of overweight and obese, and for the percent with private insurance compared to the data reported in the Kohn article.

```{stata}
use "NHANES0708_all.dta"

tabout age_3cat race_eth bmicat food_any if subpop2==1 & male==1 using "T1.csv", c(freq col) f(0 1) replace
```























