---
title: "Exercise 7 - EPI536-Assignments"
author: "Matthew Hoctor"
date: "7/6/2021"
output:
  html_document:
    number_sections: no
    theme: lumen
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(engine.path = list(
  stata = "C:/Program Files/Stata17/StataBE-64"
))
```

```{r libraries, include=FALSE}
library(Statamarkdown)
```

# I: Univariate Analysis

## 1: Examine exposure: food assistance

### a: tabulating food security and food assistance

```{stata}
use "NHANES0708_all.dta"

ta food_any foodinsec
```

## 2: Examine outcome: BMI z-score

Analysis limited to food secure boys.

### a: Calculate descriptive Statistics

```{stata}
use "NHANES0708_all.dta"

svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

su ridageyr if subpop2==1 & male==1 & foodinsec==0
svy,subpop(if subpop2==1 & male==1 & foodinsec==0): mean ridageyr

tabstat ridageyr [aweight=wtmec2yr] if subpop2==1 & male==1 & foodinsec==0, stat(p50 p10 p90) col(stat)

sktest ridageyr [aweight=wtmec2yr] if subpop2==1 & male==1 & foodinsec==0
```

### b: Create a histogram and box plot

```{stata}
use "NHANES0708_all.dta"

hist bmiz if subpop2==1 & male==1 & foodinsec==0,norm

graph export BMI-z_hist.svg, replace
```

```{stata}
use "NHANES0708_all.dta"

graph box bmiz if subpop2==1 & male==1 & foodinsec==0

graph export BMI-z_boxplot.svg, replace
```

<embed src="BMI-z_hist.svg" type="image/svg+xml" />
<embed src="BMI-z_boxplot.svg" type="image/svg+xml" />


## 3: Examine other independant variables

Analysis limited to food secure boys.

### a: Age

#### Calculate descriptive statistics

```{stata}
use "NHANES0708_all.dta"

svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

su ridageyr if subpop2==1 & male==1 & foodinsec==0
svy,subpop(if subpop2==1 & male==1 & foodinsec==0): mean ridageyr

tabstat ridageyr [aweight=wtmec2yr] if subpop2==1 & male==1 & foodinsec==0, stat(p50 p10 p90) col(stat)

sktest ridageyr [aweight=wtmec2yr] if subpop2==1 & male==1 & foodinsec==0
```

#### Create a histogram and box plot

```{stata}
use "NHANES0708_all.dta"

hist ridageyr if subpop2==1 & male==1 & foodinsec==0,norm

graph export age_hist.svg, replace
```

```{stata}
use "NHANES0708_all.dta"

graph box ridageyr if subpop2==1 & male==1 & foodinsec==0

graph export age_boxplot.svg, replace
```

<embed src="age_hist.svg" type="image/svg+xml" />
<embed src="age_boxplot.svg" type="image/svg+xml" />

### b: categorical variables

```{stata}
use "NHANES0708_all.dta"

ta fpl_2cat if subpop2==1 & male==1 & foodinsec==0

ta hinsur if subpop2==1 & male==1 & foodinsec==0
```

# II: Bivariate Analysis

For the questions in this section, limit the analyses to food secure boys.

## 1: cross-tabulation of categorical independent variables with high waist circumfrence

```{stata}
use "NHANES0708_all.dta"

ta fpl_2cat if subpop2==1 & male==1 & foodinsec==0

ta hinsur if subpop2==1 & male==1 & foodinsec==0
```

## 2: 10th and 90th percentile values of  continuous independent variables within each category of the dependent variable (high waist circumference).  


## 3: Cross-tabulate example categorical independent variables with the exposure variable, food assistance.



## 4: Calculate 10th and 90th percentile values of an example continuous covariate within each category of the exposure (food assistance), among food secure boys.







