---
title: "Exercise 9 - EPI536-Assignments"
author: "Matthew Hoctor"
date: "7/12/2021"
output:
  html_document:
    number_sections: no
    theme: lumen
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(engine.path = list(
  stata = "C:/Program Files/Stata17/StataBE-64"
))
```

```{r libraries, include=FALSE}
library(Statamarkdown)
```

# 1: Age Quintiles

Create age quintiles (weighted, in entire subpop2 sample).  Report the range and median (midpoint) of each quintile (also weighted).

```{stata}
use "NHANES0708_all.dta"

svyset sdmvpsu [pw=wtmec2yr], strata(sdmvstra)

xtile age_q5=ridageyr [aweight=wtmec2yr] if subpop2==1,nq(5)

bysort age_q5: tabstat ridageyr [aweight=wtmec2yr],stat(n min max p50)
```

# 2 Run the crude model with the categorical quintile variable.

# 3 Run the crude model with the linear age term.

# 4 How closely does the linear relationship align with the quintiles?

# 5 Test higher order terms: quadratic and cubic models

# Bonus

## Lowess

```{stata}
use "C:\Users\Matt\Documents\EPI536\Assignments\NHANES0708_all.dta"

lowess wccata ridageyr if subpop2==1 & male==1 & foodinsec==0,logit

graph export lowess.svg, replace
```

<embed src="lowess.svg" type="image/svg+xml" />

## nlcheck

```{stata}
use "NHANES0708_all.dta"

xi: logit wccata ridageyr if subpop2==1 & male==1 & foodinsec==0
nlcheck ridageyr,graph
graph export nlcheck.svg, replace
```

<embed src="nlcheck.svg" type="image/svg+xml" />

# Stata Code Accompanying the assignment

```{stata}
# *Stata-generated plot
# 
# *Create quintile variable
# xtile prage_q5=dmdhrage [aweight=wtmec2yr] if subpop2==1,nq(5)
# 
# *Create centered variable
# svy,subpop(subpop2): mean dmdhrage
# *mean PR age: 39.0
# gen pragec=dmdhrage-39
# *Create higher order terms
# gen pragec_sq=pragec^2
# gen pragec_cb=pragec^3
# 
# *Run model with age quintiles
# xi: svy,subpop(if subpop2==1 & male==0 & foodinsec==0): logit wccata i.prage_q5
# predict pred_wc2_q5,xb
# predict pred_wc2_se_q5,stdp
# gen pred_wc2_ub_q5=pred_wc2_q5 + 1.96*pred_wc2_se_q5
# gen pred_wc2_lb_q5=pred_wc2_q5 - 1.96*pred_wc2_se_q5
# 
# *Run model with linear age
# xi: svy,subpop(if subpop2==1 & male==0 & foodinsec==0): logit wccata dmdhrage
# predict pred_wc2_x,xb
# *Run model with quadratic age
# xi: svy,subpop(if subpop2==1 & male==0 & foodinsec==0): logit wccata pragec pragec_sq
# predict pred_wc2_sq,xb
# 
# twoway scatter pred_wc2_q5 dmdhrage if subpop2==1 & male==0 & foodinsec==0, mcolor(blue) ///
# 	|| scatter pred_wc2_lb_q5 dmdhrage if subpop2==1 & male==0 & foodinsec==0, msymbol(smx) mcolor(blue) ///
# 	|| scatter pred_wc2_ub_q5 dmdhrage if subpop2==1 & male==0 & foodinsec==0, msymbol(smx) mcolor(blue) ///
# 	|| scatter pred_wc2_x dmdhrage if subpop2==1 & male==0 & foodinsec==0 ///
# 	|| scatter pred_wc2_sq dmdhrage if subpop2==1 & male==0 & foodinsec==0
# 	

```





